### 2021-05-17 main.tex
more main

In the following, we will describe these entities, activities, and relations and discuss the information that should be included in \webprov{}.
% "In the following"?
For each provenance entity and activity, we will show examples of our specialization with provenance information obtained from the provenance graph of the simulation study by \lee{}~\cite{Lee2003}, shown in Fig~\ref{fig:ProvLee}.

@@

As for the provenance example shown in Fig~\ref{fig:ProvLee}, \lee{}~\cite{Lee2003} questioned in \texttt{RQ1} the necessity of \enquote{the two scaffold proteins, APC and Axin} (for \wnt{} signaling) and whether \enquote{their roles differ}.
This research question determines a minimum number of model constituents and guides the modeler towards possible simulation experiments to be executed.
% "model constituents"?

@@

\noindent The simulation model is the actual mathematical or computational model~\cite{Fisher2007} that can be executed by a suitable tool.
In most cases of our domain, the simulation model contains equations (for ODE/PDE systems) or, in some cases, reaction rules (for rule-based systems).
An integral part of these quantitative simulation models are the parameter values as well as the initial condition.
The simulation model could also be described in another form (e.g., in a quantitative process algebra~\cite{Ciocchetta2009, Boemo2020} or with a combination of multiple formalisms~\cite{Karr2015}.
% TODO no end to "("
Formal approaches to describe a system through qualitative models (e.g., Boolean models~\cite{Wang2012} or Petri nets~\cite{Chaouiya2007}) come with their own means of analysis and are assigned to the \SM{} entity as they are executable models.
Usually, a parameter table complements the description of the simulation model and gives information about the parameter values and their origin.

@@

\noindent The simulation experiment is an execution of the simulation model.
Ideally, it can be linked to a complete experiment specification (e.g., as a SED-ML~\cite{Koehn2008} or SESSL~\cite{Ewald2014} file or simply as the execution code in a general purpose programming language) and to documentation in a standard format that applies reporting guidelines such as MIASE for simulation experiments~\cite{Waltemath2011}.
Diverse simulation experiments might be applied to serve the analysis, calibration, and validation of a simulation model.
% "to serve"?

To further structure the set of simulation experiments applied, we distinguish simulation experiments by whether they are used for optimization, sensitivity analysis, perturbation, parameter scan, steady-state analysis, or time course analysis.
% what does it mean by "experiments applied"? also should it be "by whether"?
This list is neither complete nor are the categories disjoint and, given a different set of simulation studies, they will likely be subject to renaming, extension, and refinement.

>>>>

In the following, we will describe these entities, activities, and relations and discuss the information that should be included in \webprov{}.
For each provenance entity and activity, we will show examples of our specialization with provenance information obtained from the provenance graph of the simulation study by \lee{}~\cite{Lee2003}, shown in Fig~\ref{fig:ProvLee}.

@@

As for the provenance example shown in Fig~\ref{fig:ProvLee}, \lee{}~\cite{Lee2003} questioned in \texttt{RQ1} the necessity of \enquote{the two scaffold proteins, APC and Axin} (for \wnt{} signaling) and whether \enquote{their roles differ}.
This research question determines a minimum number of model constituents and guides the modeler towards possible simulation experiments to be executed.

@@

\noindent The simulation model is the actual mathematical or computational model~\cite{Fisher2007} that can be executed by a suitable tool.
In most cases of our domain, the simulation model contains equations (for ODE/PDE systems) or, in some cases, reaction rules (for rule-based systems).
An integral part of these quantitative simulation models are the parameter values as well as the initial condition.
The simulation model could also be described in another form (e.g., in a quantitative process algebra~\cite{Ciocchetta2009, Boemo2020} or with a combination of multiple formalisms~\cite{Karr2015}.
Formal approaches to describe a system through qualitative models (e.g., Boolean models~\cite{Wang2012} or Petri nets~\cite{Chaouiya2007}) come with their own means of analysis and are assigned to the \SM{} entity as they are executable models.
Usually, a parameter table complements the description of the simulation model and gives information about the parameter values and their origin.

@@

\noindent The simulation experiment is an execution of the simulation model.
Ideally, it can be linked to a complete experiment specification (e.g., as a SED-ML~\cite{Koehn2008} or SESSL~\cite{Ewald2014} file or simply as the execution code in a general purpose programming language) and to documentation in a standard format that applies reporting guidelines such as MIASE for simulation experiments~\cite{Waltemath2011}.
Diverse simulation experiments might be applied to serve the analysis, calibration, and validation of a simulation model.

To further structure the set of applied simulation experiments, we distinguish simulation experiments by whether they are used for optimization, sensitivity analysis, perturbation, parameter scan, steady-state analysis, or time course analysis.
This list is neither complete nor are the categories disjoint and, given a different set of simulation studies, they will likely be subject to renaming, extension, and refinement.
